---
title: "Econ 4"
author: "Gracie White"
date: "6/2/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, include=FALSE}

library(tidyverse)
library(kableExtra)


carbon <- read_csv("HW4DATA.csv")

```
The data contain
estimates of the marginal cost of carbon abatement for four economic sectors (sectors A, B, C, and D). A few
notes:
 Current carbon emissions in the sectors are: (A=180, B=200, C=220, and D=300).
 Sectors A, B, and C are in country X. Sector D is in a different country, Y.
 Prices are in $/ton and quantities are in tons.

###1. 
Write down a plausible functional form for the marginal cost of abatement for sector A. Use regression
analysis to estimate the parameters of that function. Repeating this for sectors B, C, and D will give
you a model of the marginal cost of abatement function for each sector. How well do your models fit
the data for each sector? You may need to experiment with different functional forms. Produce a plot
of the estimated marginal abatement cost functions in all four sectors (this plot should go in your
memo).


```{r, echo=FALSE}

#figure out appropriate model forms with basic plots 

graph_a <- ggplot(carbon, aes(x = Abatement, y = MC_A)) +
  geom_point()
graph_a

#Sector A looks linear, perhaps slightly logistic
#I'll do a logistic model just because 

model_A <- glm(Abatement ~ MC_A, data = carbon)
summary(model_A)
#I think using linear throughout will just be easier. Sam said that was fine and I can't be bothered to go above and beyond rn. 

a_lm <- lm(MC_A ~ Abatement, data=carbon)
# Store coefficients of regression
int_a <- a_lm$coefficients[1]
slope_a <- a_lm$coefficients[2]

#store function
curve_a <- function(x){int_a + slope_a*x}


graph_b <- ggplot(carbon, aes(x = Abatement, y = MC_B)) +
  geom_point()
graph_b
#Linear Enough 
b_lm <- lm(MC_B ~ Abatement, data = carbon)
int_b <- b_lm$coefficients[1]
slope_b <- b_lm$coefficients[2]
#store function
curve_b <- function(x){int_b + slope_b*x}

graph_c <- ggplot(carbon, aes(x = Abatement, y = MC_C)) +
  geom_point()
graph_c
#linear enough, perhaps slightly exponential
c_lm <- lm(MC_C ~ Abatement, data = carbon)
int_c <- c_lm$coefficients[1]
slope_c <- c_lm$coefficients[2]
#store function
curve_c <- function(x){int_c + slope_c*x}

graph_d <- ggplot(carbon, aes(x = Abatement, y = MC_D)) +
  geom_point()
graph_d
#Linear enough, I'm over it.
d_lm <- lm(MC_D ~ Abatement, data = carbon)
int_d <- d_lm$coefficients[1]
slope_d <- d_lm$coefficients[2]
#store function
curve_d <- function(x){int_d + slope_d*x}



```

$Marginal~Cost~Abatement~Sector~A = `r slope_a`*q + `r int_a`$ 
$Marginal~Cost~Abatement~Sector~B = `r slope_b`*q + `r int_b`$
$Marginal~Cost~Abatement~Sector~C = `r slope_c`*q + `r int_c`$
$Marginal~Cost~Abatement~Sector~D = `r slope_d`*q + `r int_d`$


```{r, echo=FALSE}

curve_plot <- ggplot(data.frame(x = c(0, 350))) + 
  stat_function(fun = curve_a, aes(color = "A")) +
  stat_function(fun = curve_b, aes(color = "B")) +
  stat_function(fun = curve_c, aes(color = "C")) +
  stat_function(fun = curve_d, aes(color = "D")) +
  scale_y_continuous(limits= c(-10,100), expand = c(0,0)) +
  scale_x_continuous(limits= c(0, 350), expand = c(0,0)) + 
  labs(fill = "", color = "Sectors") + 
  xlab("\n Carbon Abatement (ton)") + 
  ylab("Marginal Cost \n($/ton) \n") + 
  theme_classic() +
  ggtitle("Marginal Cost of Abatement\n") +
  theme(plot.title = element_text(hjust = 0.5),
        axis.title.y = element_text(angle=0, hjust = 0.5, vjust = 0.5)) 
curve_plot

```

###2. 
Using these models and the current level of carbon emissions, derive each sector’s demand curve for
carbon emissions. In other words, how much would each sector be willing to pay for the right to
pollute the first unit, second unit, etc? Draw these demand curves on a graph. Which sector is willing to
pay the most for the first unit of carbon emissions?


```{r}

#Sector A - Current Emissions = 180

quant_a <- seq(0,180,by=10)
curve_d_a <- function(q){
  (slope_a*(180-q)) + int_a
}
demand_a <- curve_d_a(quant_a)
curve(curve_d_a, from=0, to=180, xlab = "x", ylab = "y") #looks like it worked. Sweet. 
demand_a 

#Sector B - Current Emissions = 200
quant_b <- seq(0,200,by=10)
curve_d_b <- function(q){
  (slope_b*(200-q)) + int_b
}
demand_b <- curve_d_b(quant_b)
curve(curve_d_b, from=0, to=200, xlab = "x", ylab = "y") #looks like it worked. Sweet. 
demand_b 

#Sector C - Current Emissions = 220

quant_c <- seq(0,220,by=10)
curve_d_c <- function(q){
  (slope_c*(200-q)) + int_c
}
demand_c <- curve_d_c(quant_c)
curve(curve_d_c, from=0, to=220, xlab = "x", ylab = "y") #looks like it worked. Sweet. 
demand_c 

#Sector D - Current Emissions = 300

quant_d <- seq(0,300,by=10)
curve_d_d <- function(q){
  (slope_d*(200-q)) + int_d
}
demand_d <- curve_d_d(quant_d)
curve(curve_d_d, from=0, to=300, xlab = "x", ylab = "y") #looks like it worked. Sweet. 
demand_d 



```


Sector A:  $Price~of~Emissions = `r slope_a`*(180-q) + `r int_a`$ 

 - Willingness to Pay for First Unit = \$95.2    
 
Sector B: $Price~of~Emissions = `r slope_b`*(200-q) + `r int_b`$
 
- Willingness to Pay for First Unit = \$49.12 

Sector C: $Price~of~Emissions = `r slope_c`*(220-q) + `r int_c`$

- Willingness to Pay for First Unit = \$145.11

Sector D: $Price~of~Emissions = `r slope_d`*(300-q) + `r int_d`$

- Willingness to Pay for First Unit = \$61.67 


Sector C is willing to pay the most. 

```{r, echo=FALSE}

demand_plot <- ggplot(data.frame(x = c(0, 350))) + 
  stat_function(fun = curve_d_a, aes(color = "A")) +
  stat_function(fun = curve_d_b, aes(color = "B")) +
  stat_function(fun = curve_d_c, aes(color = "C")) +
  stat_function(fun = curve_d_d, aes(color = "D")) +
  scale_y_continuous(limits= c(-10,150), expand = c(0,0)) +
  scale_x_continuous(limits= c(0, 350), expand = c(0,0)) + 
  labs(fill = "", color = "Sectors") + 
  xlab("\n Carbon Abatement (ton)") + 
  ylab("Marginal Cost \n($/ton) \n") + 
  theme_classic() +
  ggtitle("Demand: Marginal Cost of Abatement\n") +
  theme(plot.title = element_text(hjust = 0.5),
        axis.title.y = element_text(angle=0, hjust = 0.5, vjust = 0.5)) 
demand_plot

```
Free Market Qs
Sector A: Q = 90
Sector B:Q = 100
Sector C:Q = 110
Sector D:Q = 150



###3. 
 Now focus on country X (which contains sectors A, B, and C). Assume there are no “co-benefits” from
carbon abatement (i.e. that there are no local pollutants that are affected by carbon abatement).
Suppose to meet the Paris Accord commitments, country X needs to cut all carbon emissions in half.
For each of the policy options listed below, derive: 

####a. Cap on carbon. 
Each sector (A, B, and C) must cut its carbon emissions by 100 tons (thus
reducing total emissions from 600 down to 300).
Current carbon emissions in the sectors are: (A=180, B=200, C=220)


```{r}
#Sector A
costa_100 <- curve_a(100) #49 mc
areaa_100 <- integrate(curve_a, lower = 0, upper = 100)$value

#Sector B
costb_100 <- curve_b(100) #29.2 mc
areab_100 <- integrate(curve_b, lower = 0, upper = 100)$value

#Sector C
costc_100 <- curve_c(100) #66.7 mc
areac_100 <- integrate(curve_c, lower = 0, upper = 100)$value

#Sector D not part of this Q


#Total Cost:
tc_100 <- areaa_100 + areab_100 + areac_100 #6698.88


```

#####(1) the total cost of meeting the target in country X

$Total~Cost = `r round(tc_100, digits = 6)`$

#####(2) the cost (or benefit) to each sector

$Cost~to~A = `r round(areaa_100)`$

$Cost~to~B = `r round(areab_100)`$

$Cost~to~C = `r round(areac_100)`$

#####(3) the tax revenue generated. 

Tax Revenue = 0



####b. Tax on carbon. 
To emit a ton of carbon in country X, you must pay a tax of $t. You will need to find the tax that accomplishes the desired reduction.

Emission functions:
$$Aggregate MC= 616.74 - Emissions / 8$$
$$Abatement_A = ( 95.75 - MC)/0.58 $$
$$Abatement_B = (49.32-MC)/ 0.2 $$
$$Abatement_C =(159.94-MC)/0.78 $$
$$Abatement_D = (87.69 - MC)/0.26$$
See Table!
```{r, echo=FALSE}

#ok so first we need to find the aggregate marginal cost curve for sectors A, B, and C


#step 1: rearrange!

q_a <- function(x){(x-int_a)/slope_a}
q_b <- function(x){(x-int_b)/slope_b}
q_c <- function(x){(x-int_c)/slope_c}

#Step 2: add functions 
q_ag <- function(x){q_a(x) + q_b(x) + q_c(x)}
#ok this was a mistake. Using Bridget's code for this part. 

MC<-(616.74-300) /8
Qa<-( 95.75 - 0)/0.58
Qb<-(49.32-0)/ 0.2
Qc<-(159.94-0)/0.78

abatea<-(95.75 - MC)/0.58 
abateb<-(49.32-MC)/ 0.2
abatec<-(159.94-MC)/0.78
totalabate<-sum(abatea, abateb, abatec)


abate<-rbind(abatea, abateb, abatec, totalabate)

taxa<-abatea*MC
taxb<-abateb*MC
taxc<-abatec*MC
totaltax<-sum(taxa, taxb, taxc)

tax<-rbind(taxa, taxb, taxc, totaltax)

costa<-MC*(Qa-abatea)*0.5
costb<-MC*(Qb-abateb)*0.5
costc<-MC*(Qc-abatec)*0.5
totalcost<-sum(costa, costb, costc)
cost<-rbind(costa, costb, costc, totalcost)

partb<- cbind(abate, cost,tax)
colnames(partb)=c("Units abated", "Cost","Tax")
row.names(partb)=c("Sector A", "Sector B", "Sector C", "Total Country X")
partb
round(partb,2)


```



c. Cap and trade. Each sector (A, B, C) is allocated carbon permits equal to their current emissions
minus 100 (same as in (a) above), thus achieving the total reduction of 300. Then, these three
sectors are allowed to trade with each other. You will need to derive the outcome of that
trading.
(1) the total cost of meeting the target in country X,
(2) the cost (or benefit) to each sector
(3) the tax revenue generated.


Equimarginal principle: firms will trade until the cost of abatement is the same between all 3 sectors. The goal is to abate 300 units of emissions, so the cost of abatement that meets the equimarginal principle is $39.59. Table below summarizes results.

```{r, echo=FALSE}
MC<-(616.74-300) /8

abatea<-( 95.75 - MC)/0.58 
abateb<-(49.32-MC)/ 0.2
abatec<-(159.94-MC)/0.78
totalabate<-sum(abatea, abateb, abatec)

abate<-rbind(abatea, abateb, abatec, totalabate)

costa<-(abatea*MC)+(abatea*(95.97-MC)*0.5)
costb<-(abateb*MC)+(abateb*(49.32-MC)*0.5)
costc<-(abatec*MC)+(abatec*(159.94-MC)*0.5)
totalcost<-sum(costa, costb, costc)
cost<-rbind(costa, costb, costc, totalcost)


partc<- cbind(abate, cost)
colnames(partc)=c("Units abated", "Cost")
row.names(partc)=c("Sector A", "Sector B", "Sector C", "Total Country X")
partc

round(partc, 1)
```

###4. 
Again, without any co-benefits, suppose that country Y (which only has one carbon-emitting sector, D) has no obligation to reduce its emissions. Country X asks country Y to enter the country X carbon market. Doing so would require country Y to put a cap on carbon emissions at its current level of emissions (300 tons), but would then allow country Y to sell carbon offsets to sectors A, B, or C. 

#####Are there any incentives for country Y to enter country X’s carbon market and to thus place a voluntary cap on its emissions? 

Sector Y might benefit from entering the international carbon market since their abatement costs are lower than Sectors A and C, so it could potentially be profitable. 

#####Are there any incentives for country X to try to attract country Y into its market?

Sector B would benefit from country Y entering the international carbon market since their abatements costs are lower, so it could potentially be profitable.

###5. 
Now assume that every ton of carbon emissions creates 1 ton of local air pollution. Local air pollution causes economic damages (health, environmental, etc.), but only in the country in which it is emitted.
Assume there are no local air pollution regulations in either country X or country Y.

####a. In a carbon cap and trade market that only covers sectors in country X, how much local air pollution would you expect in country X? In country Y?
Both are emitting 300 tons, so both countires would also emit 300 tons of air polluntion. 

####b. If country Y enters the carbon market for country X (as in question 4 above), how much local pollution will there be in country X and country Y?

$Aggregate MC= 954.01 - Abatement / 11.85$
```{r}
MC<-(954.01-600) /11.85
MC #29.87
300-222 #78

(87.69 - 39.59)/0.26
abatea<-(95.75 - MC)/0.58 
abateb<-(49.32-MC)/ 0.2
abatec<-(159.94-MC)/0.78
abated<-(87.69 - MC)/0.26

totalabate<-sum(abatea, abateb, abatec, abated)
abate<-rbind(abatea, abateb, abatec, abated, totalabate)
abate


costa<-(abatea*MC)+(abatea*(95.97-MC)*0.5)
costb<-(abateb*MC)+(abateb*(49.32-MC)*0.5)
costc<-(abatec*MC)+(abatec*(159.94-MC)*0.5)
costd<-(abated*MC)+(abated*(87.69-MC)*0.5)

totalcost<-sum(costa, costb, costc, costd)
cost<-rbind(costa, costb, costc, costd, totalcost)

part5<- cbind(abate, cost)
colnames(part5)=c("Units abated", "Cost")
row.names(part5)=c("Sector A", "Sector B", "Sector C", "Sector D","Total")
part5

round(part5,2)
```
If country Y enters the international carbon market this would change the cost of abatement to $29.87. Country Y would pollute 222 tons and Country X would pollute 378, and they same amount of emiisions. 600 tons in total, but more in Country X and less than Country Y. Country Y is better off in this regard. 


####c. What advice can you give country X and country Y about the desirability of allowing international trade of carbon emissions credits?


Not a great deal for country y, but it could be a good deal for country Y. 
