---
title: "Econ 4"
author: "Gracie White"
date: "6/2/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, include=FALSE}

library(tidyverse)
library(kableExtra)


carbon <- read_csv("HW4DATA.csv")




```
The data contain
estimates of the marginal cost of carbon abatement for four economic sectors (sectors A, B, C, and D). A few
notes:
 Current carbon emissions in the sectors are: (A=180, B=200, C=220, and D=300).
 Sectors A, B, and C are in country X. Sector D is in a different country, Y.
 Prices are in $/ton and quantities are in tons.

1. Write down a plausible functional form for the marginal cost of abatement for sector A. Use regression
analysis to estimate the parameters of that function. Repeating this for sectors B, C, and D will give
you a model of the marginal cost of abatement function for each sector. How well do your models fit
the data for each sector? You may need to experiment with different functional forms. Produce a plot
of the estimated marginal abatement cost functions in all four sectors (this plot should go in your
memo).


```{r, echo=FALSE}

#figure out appropriate model forms with basic plots 

graph_a <- ggplot(carbon, aes(x = Abatement, y = MC_A)) +
  geom_point()
graph_a

#Sector A looks linear, perhaps slightly logistic
#I'll do a logistic model just because 

model_A <- glm(Abatement ~ MC_A, data = carbon)
summary(model_A)
#I think using linear throughout will just be easier. Sam said that was fine and I can't be bothered to go above and beyond rn. 

a_lm <- lm(MC_A ~ Abatement, data=carbon)
# Store coefficients of regression
int_a <- a_lm$coefficients[1]
slope_a <- a_lm$coefficients[2]

#store function
curve_a <- function(x){int_a + slope_a*x}


graph_b <- ggplot(carbon, aes(x = Abatement, y = MC_B)) +
  geom_point()
graph_b
#Linear Enough 
b_lm <- lm(MC_B ~ Abatement, data = carbon)
int_b <- b_lm$coefficients[1]
slope_b <- b_lm$coefficients[2]
#store function
curve_b <- function(x){int_b + slope_b*x}

graph_c <- ggplot(carbon, aes(x = Abatement, y = MC_C)) +
  geom_point()
graph_c
#linear enough, perhaps slightly exponential
c_lm <- lm(MC_C ~ Abatement, data = carbon)
int_c <- c_lm$coefficients[1]
slope_c <- c_lm$coefficients[2]
#store function
curve_c <- function(x){int_c + slope_c*x}

graph_d <- ggplot(carbon, aes(x = Abatement, y = MC_D)) +
  geom_point()
graph_d
#Linear enough, I'm over it.
d_lm <- lm(MC_D ~ Abatement, data = carbon)
int_d <- d_lm$coefficients[1]
slope_d <- d_lm$coefficients[2]
#store function
curve_d <- function(x){int_d + slope_d*x}



```

$Marginal~Cost~Abatement~Sector~A = `r slope_a`*q + `r int_a`$ 
$Marginal~Cost~Abatement~Sector~B = `r slope_b`*q + `r int_b`$
$Marginal~Cost~Abatement~Sector~C = `r slope_c`*q + `r int_c`$
$Marginal~Cost~Abatement~Sector~D = `r slope_d`*q + `r int_d`$


```{r, echo=FALSE}

curve_plot <- ggplot(data.frame(x = c(0, 350))) + 
  stat_function(fun = curve_a, aes(color = "A")) +
  stat_function(fun = curve_b, aes(color = "B")) +
  stat_function(fun = curve_c, aes(color = "C")) +
  stat_function(fun = curve_d, aes(color = "D")) +
  scale_y_continuous(limits= c(-10,100), expand = c(0,0)) +
  scale_x_continuous(limits= c(0, 350), expand = c(0,0)) + 
  labs(fill = "", color = "Sectors") + 
  xlab("\n Carbon Abatement (ton)") + 
  ylab("Marginal Cost \n($/ton) \n") + 
  theme_classic() +
  ggtitle("Marginal Cost of Abatement\n") +
  theme(plot.title = element_text(hjust = 0.5),
        axis.title.y = element_text(angle=0, hjust = 0.5, vjust = 0.5)) 
curve_plot

```


